---
title: "Homework3"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(webshot)
```

```{r library-packages}
library(httr)
library(rvest)
library(tidyverse)
library(stringr)
library(tidytext)
library(forcats)
```


1. Using the NCBI API, look for papers that show up under the term “sars-cov-2 trial vaccine” Look for the data in the pubmed database, and then retrieve the details of the paper as shown in lab 7. How many papers were you able to find?

a). How many papers we are able to find under the term “sars-cov-2 trial vaccine”.
```{r}
# Downloading the website
website <- xml2::read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine")
# Finding the counts
counts <- xml2::xml_find_first(website, "/html/body/main/div[9]/div[2]/div[2]/div[1]/div[1]/span")
# Turning it into text
counts <- as.character(counts)
# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```

b) Query first. Query parameters:
database: pubmed
term: sars-cov-2 trial vaccine
retmax: 1000
```{r}
query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(
    db      = "pubmed",
    term    ="sars-cov-2 trial vaccine",
    retmax  = 1000
  ), 
)

# Extracting the content of the response of GET
ids <- httr::content(query_ids)
```

c) Get details about the articles.
```{r}
# Turn the result into a character vector
ids <- as.character(ids)
# Find all the ids 
ids <- stringr::str_extract_all(ids, "<Id>[[:digit:]]+</Id>")[[1]]
# Remove all the leading and trailing <Id> </Id>. Make use of "|"
ids <- stringr::str_remove_all(ids, "</?Id>")
head(ids)
```

2. Using the list of pubmed ids you retrieved, download each papers’ details using the query parameter rettype = abstract. If you get more than 250 ids, just keep the first 250.
```{r}
publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
    db  = "pubmed",
    id  = paste(ids,collapse = ","),
  retmax = 250,
  rettype = "abstract"
    )
)

publications <- httr::content(publications)
publication_txt <- as.character(publications)
```



