---
title: "Homework1"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
always_allow_html:true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(webshot)
```

1. EDA Checklist 2-4:
a). Read in your data:read in the data using data.table()
```{r read-data}
library(readr)
library(dplyr)
pm_2004 <- data.table::fread("ad_viz_plotval_data-2004.csv")
pm_2019 <- data.table::fread("ad_viz_plotval_data-2019.csv")
```

b).  For each of the two datasets, check the dimensions, headers, footers, variable names and variable types.
```{r 2004-data}
dim(pm_2004)
head(pm_2004)
tail(pm_2004)
str(pm_2004)
```
```{r 2019-data}
dim(pm_2019)
head(pm_2019)
tail(pm_2019)
str(pm_2019)
```

c). Check for any data issues, particularly in the key variable we are analyzing.
```{r}
table(pm_2004$`Daily Mean PM2.5 Concentration`)
```
```{r}
table(pm_2019$`Daily Mean PM2.5 Concentration`)
```

```{r}
summary(pm_2004$`Daily Mean PM2.5 Concentration`)
summary(pm_2019$`Daily Mean PM2.5 Concentration`)
```
Summary: 
  1) For dimension, two datasets have same number of columns but 2019 data has much more rows.
  2) I notice that there are negative values for 'Daily Mean PM2.5 Concentration'. This is the main issue of theses datasets.
  3) Most of summary value for 2004 data is higher than 2019 data.

2. 
a). Combine the two years of data into one data frame
```{r}
pm <- rbind(pm_2004, pm_2019)
head(pm)
tail(pm)
```
b) Use the Date variable to create a new column for year, which will serve as an identifier. 
```{r}
library(lubridate)
Date = as.Date.character(pm$Date, "%m/%d/%Y")
Year <- year(Date)
pm <- mutate(pm, Year)
head(pm)
```
 c) Change the names of the key variables so that they are easier to refer to in your code.
```{r}
library(tidyverse)
pm<-rename(pm, PM2.5_Concentration = 'Daily Mean PM2.5 Concentration')
```
 3. 
 a). Create a basic map in leaflet() that shows the locations of the sites (make sure to use different colors for each year)
```{r}
library(leaflet)
pal <- colorFactor(c('red', 'blue'), domain=pm$Year)
map <- leaflet(pm) %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lng=pm$SITE_LONGITUDE, lat=pm$SITE_LATITUDE, opacity=1, fillOpacity=1, radius = 50, color = ~pal(Year))
map
```
 
 b). Summarize the spatial distribution of the monitoring sites.
From the map, we can find that there are great number of sites gathering in Los Angeles district and San Jose district. And the distribution range is all over California. 

4. 
a). Check for any missing or implausible values of PM in the combined dataset. 
As we mentioned before, we have negative values for concentration in the dataset.
```{r}
table(pm$PM2.5_Concentration)
is.na(pm$PM2.5_Concentration)
```
It seems like no NA in this column.

b). Explore the proportions of each and provide a summary of any temporal patterns you see in these observations.

```{r}
negative <- pm[pm$PM2.5_Concentration <0]
proportions = nrow(negative)/nrow(pm)
proportions
```
From the calculation above, the proportions of negative value is 0.39%.It is a tiny proportion. 

