---
title: "Homework2"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(webshot)
```

```{r library-packages}
library(lubridate)
library(tidyverse)
library(data.table)
library(dtplyr)
library(dplyr)
library(ggplot2)
```


Data Wrangling
```{r read-data}
if (!file.exists("/Users/apple/Desktop/pm566/PM566-Homework/homework 2/chs_individual.csv")){
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/01_chs/chs_individual.csv", "chs_individual.csv", method="libcurl", timeout = 60)
}
individual <- data.table::fread("/Users/apple/Desktop/pm566/PM566-Homework/homework 2/chs_individual.csv")

if (!file.exists("/Users/apple/Desktop/pm566/PM566-Homework/homework 2/chs_regional.csv")){
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/01_chs/chs_regional.csv", "chs_regional.csv", method="libcurl", timeout = 60)
}
individual <- data.table::fread("/Users/apple/Desktop/pm566/PM566-Homework/homework 2/chs_individual.csv")
regional <- data.table::fread("/Users/apple/Desktop/pm566/PM566-Homework/homework 2/chs_regional.csv")
```

```{r merge-data}
data<-
  merge(
    x= individual,
    y= regional,
    by.x = "townname",
    by.y = "townname",
    all.x = TRUE,
    all.y = FALSE
  )
```

1. After merging the data, make sure you don’t have any duplicates by counting the number of rows. Make sure it matches.
```{r}
nrow(data)
nrow(individual)
#We find that "data" and "individual" have same number of rows. There is no duplicates.
```

In the case of missing values, impute data using the average within the variables “male” and “hispanic.” 
```{r}
data[ , bmi_imp := fcoalesce(bmi, mean(bmi, na.rm = TRUE)),
      by = .(male , hispanic)]
data[ , fev_imp := fcoalesce(fev, mean(fev, na.rm = TRUE)),
      by = .(male , hispanic)]
```

2. Create a new categorical variable named “obesity_level” using the BMI measurement (underweight BMI<14; normal BMI 14-22; overweight BMI 22-24; obese BMI>24). 
```{r}
data[, 
    obesity_level := 
      case_when(bmi_imp < 14 ~ "Underweight",
                bmi_imp >= 13 & bmi_imp <22 ~ "Normal",
                bmi_imp >= 22 & bmi_imp < 24 ~ "Overweight",
                bmi_imp >24 ~"Obese")
]
head(data)
```

To make sure the variable is rightly coded, create a summary table that contains the minimum BMI, maximum BMI, and the total number of observations per category.
```{r}
data%>%
group_by(obesity_level)%>%
summarise(
  min_bmi = min(bmi_imp, na.rm = TRUE),
  max_bmi = max(bmi_imp, na.rm = TRUE),
  total_obs = n()) %>%
knitr::kable()
```

3. Create another categorical variable named “smoke_gas_exposure” that summarizes “Second Hand Smoke” and “Gas Stove.” The variable should have four categories in total.
```{r}
data[, 
    smoke_gas_exposure := 
      case_when(smoke == 0 & gasstove == 0 ~ "no exposure",
                smoke == 1 & gasstove == 0  ~ "smoke exposure",
                smoke == 0 & gasstove == 1 ~ "gas exposure",
                smoke == 1 & gasstove == 1 ~ "both exposure")
]
head(data)
```
4. Create four summary tables showing the average (or proportion, if binary) and sd of “Forced expiratory volume in 1 second (ml)” and asthma indicator by town, sex, obesity level, and “smoke_gas_exposure.”

```{r by-town}
data[ , .(
  avg_fev1 = mean(fev_imp, na.rm= TRUE),
  sd_fev1 = sd(fev_imp, na.rm = TRUE),
  percent_asthma = sum(asthma, na.rm = TRUE)/sum(!is.na(asthma))),
  by = townname][order(townname)]%>% head(n=10)
```

```{r by-sex}
data[ , .(
  avg_fev1 = mean(fev_imp, na.rm= TRUE),
  sd_fev1 = sd(fev_imp, na.rm = TRUE),
  percent_asthma = sum(asthma, na.rm = TRUE)/sum(!is.na(asthma))),
  by = male][order(male)]%>% head(n=10)
```
```{r by-obesity_level}
data[ , .(
  avg_fev1 = mean(fev_imp, na.rm= TRUE),
  sd_fev1 = sd(fev_imp, na.rm = TRUE),
  percent_asthma = sum(asthma, na.rm = TRUE)/sum(!is.na(asthma))),
  by = obesity_level][order(obesity_level)]%>% head(n=10)
```

```{r by-smoke_gas_exposure}
data[ , .(
  avg_fev1 = mean(fev_imp, na.rm= TRUE),
  sd_fev1 = sd(fev_imp, na.rm = TRUE),
  percent_asthma = sum(asthma, na.rm = TRUE)/sum(!is.na(asthma))),
  by = smoke_gas_exposure][order(smoke_gas_exposure)]%>% head(n=10)
```

Looking at the Data (EDA)
The primary questions of interest are:
1. What is the association between BMI and FEV (forced expiratory volume)? 
2. What is the association between smoke and gas exposure and FEV?
3. What is the association between PM2.5 exposure and FEV?

Follow the EDA checklist from week 3 and the previous assignment. Be sure to focus on the key variables.
```{r}
#check the dimensions, headers, footers, variable names and variable types
dim(data)
head(data)
tail(data)
str(data)
```

```{r}
# Check for any data issues, particularly in the key variable we are analyzing.
table(data$bmi_imp)
summary(data$bmi_imp)
table(data$fev_imp)
summary(data$fev_imp)
table(data$smoke_gas_exposure)
summary(data$smoke_gas_exposure)
table(data$pm25_mass)
summary(data$pm25_mass)
```

Visualization Create the following figures and interpret them. Be sure to include easily understandable axes, titles, and legends.

1. Facet plot showing scatterplots with regression lines of BMI vs FEV by “townname”.
```{r}
data[!is.na(bmi_imp)& !is.na(fev_imp)] %>% 
  ggplot(mapping = aes(x= fev_imp,y=bmi_imp)) + 
  geom_point(mapping=aes(color=townname)) + 
  geom_smooth(method = lm, mapping = aes(linetype=townname))+
facet_wrap(~townname, nrow=4)
```

2. Stacked histograms of FEV by BMI category and FEV by smoke/gas exposure. Use different color schemes than the ggplot default.
```{r}
ggplot(data, aes(fev_imp, fill= obesity_level))+ geom_histogram(binwidth=300)+ggtitle("Histogram of FEV by obesity level category")+scale_fill_brewer(palette = 3)
```
```{r}
ggplot(data, aes(fev_imp, fill= smoke_gas_exposure))+ geom_histogram(binwidth=200)+ggtitle("Histogram of FEV by gas&smoke exposure category")+scale_fill_brewer(palette = 5)
```
3. Barchart of BMI by smoke/gas exposure.
```{r}
data%>%
ggplot(mapping = aes(x= obesity_level, fill = smoke_gas_exposure))+geom_bar()+ggtitle("Barchart of BMI by smoke&gas exposure")
```

4. Statistical summary graphs of FEV by BMI and FEV by smoke/gas exposure category.
```{r}
data%>%
ggplot()+stat_summary(mapping=aes(x=obesity_level, y= fev_imp),
                      fun.data = mean_sdl)+ggtitle("Statistical summary graphs of FEV by obesity level")
```

```{r}
data%>%
ggplot()+stat_summary(mapping=aes(x=smoke_gas_exposure, y= fev_imp),
                      fun.data = mean_sdl)+ggtitle("Statistical summary graphs of fev by smoke&gas exposure")

```
5. A leaflet map showing the concentrations of PM2.5 mass in each of the CHS communities.
```{r}
library(leaflet)
pal <- colorFactor(c('red', 'blue'), domain= data$pm25_mass)
map <- leaflet(data) %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lng=data$lon, lat=data$lat, opacity=1, fillOpacity=1, radius = 50, color = ~pal(data$pm25_mass))
map
```

6. Choose a visualization to examine whether PM2.5 mass is associated with FEV
```{r}
ggplot(data=data)+geom_point(mapping=aes(x=fev_imp, y=pm25_mass))+ggtitle("pm2.5 mass with FEV")
```

Conclusion:with the increase of pm2.5 mass, the fev level lightly decreases.