---
title: "Homework4"
author: "Chen Chen 6381370662"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(webshot)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```

# HPC

## Problem 1: Make sure your code is nice
Rewrite the following R functions to make them faster. It is OK (and recommended) to take a look at Stack overflow and Google
```{r}
# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}

fun1alt <- function(mat) {
  rowSums(mat)
}

# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}

fun2alt <- function(mat) {
  t(apply(mat, 1, cumsum))
}


# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)

# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), check = "equivalent"
)

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), check = "equivalent"
)
```

Comparison: It is obvious that the time cost by fun1&2alt is shorter than cost by fun1&2. 

## Problem 2: Make things run faster with parallel computing
The following function allows simulating PI
```{r}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132
```

In order to get accurate estimates, we can run this function multiple times, with the following code:
```{r}
# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})
```

Rewrite the previous code using parLapply() to make it run faster. Make sure you set the seed using clusterSetRNGStream():
```{r}
library(parallel)
cl<- makePSOCKcluster(4)
clusterSetRNGStream(cl, 1231)
clusterExport(cl, c("sim_pi"), envir=environment())

system.time({
  ans <- unlist(parLapply(cl, 1:4000, sim_pi, n=10000))
  print(mean(ans))
})
```

Comparison: It is obvious that the time by code re-written is lesser than the original one.

# SQL
Setup a temporary database by running the following chunk
```{r}
# install.packages(c("RSQLite", "DBI"))
if(!require(RSQLite))install.packages(c("RSQLite"))
if(!require(DBI))install.packages(c("DBI"))
library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)
```

## Question 1
How many many movies is there available in each rating category.
```{sql, connection= con}
PRAGMA table_info(film)
```

```{sql, connection= con}
SELECT rating,
  COUNT(*) AS movie_count
FROM film
GROUP BY rating
```

## Question 2
What is the average replacement cost and rental rate for each rating category.
```{sql, connection= con}
SELECT rating,
       AVG(replacement_cost) AS avg_replacement_cost,
       AVG(rental_rate) AS avg_rental_rate
FROM film
GROUP BY rating
```

## Question 3
Use table film_category together with film to find the how many films there are with each category ID
```{sql, connection= con}
PRAGMA table_info(film_category)
```

```{sql, connection= con}
SELECT c.category_id,
       count(*) AS film_count
FROM film_category AS c INNER JOIN film AS f
ON c.film_id = f.film_id
GROUP BY category_id
```

## Question 4
Incorporate table category into the answer to the previous question to find the name of the most popular category.
```{sql, connection= con}
PRAGMA table_info(category)
```

```{sql, connection= con}
SELECT a.category_id,
       c.name,
       count(*) AS film_count
FROM film_category AS a
INNER JOIN film AS f ON a.film_id = f.film_id
INNER JOIN category AS c ON a.category_id = c.category_id
GROUP BY a.category_id
ORDER BY film_count DESC
```
From the table above, the  most popular category is sports with category id 15. 

